---
title: "project"
author: "jack"
date: "20/07/2021"
output: html_document
---
data from https://doi.org/10.26197/ala.3bf1b394-8646-4e3e-99d9-0ef7a5258d35


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup}
library (galah)
library (stringr)
library (rgdal)
library(sf)
library(maps)
library(mapdata)
library(dplyr)
library(tidyr)
library(ggplot2)

```

data from ALA for Eucalypts

```{r pressure, echo=FALSE}
library(readr)
records.2021.07.21 <- read.csv("~/Documents/R/bigdata/project/records-2021-07-21/records-2021-07-21.csv")
View(records.2021.07.21)
```


```{r}
#plot data on a map to get initial view
library(ggplot2)
wm <- borders("world", colour="slategray1", fill="slategray1")
ggplot()+ coord_fixed()+ wm +
  geom_point(data = records.2021.07.21, aes(x = decimalLongitude, y = decimalLatitude),
             colour = "green", size = 0.5)+
  theme_bw()
```


```{r} 
#now clean with coordinate cleaner 
library(countrycode)
library(CoordinateCleaner)
library(rgbif)
library(sp)
library(dplyr)
```

```{r}
#columns of interest
records_filter_1 <- records.2021.07.21 %>%
  dplyr::select(species, decimalLongitude, decimalLatitude, countryCode, individualCount,
         family, taxonRank, coordinateUncertaintyInMeters, year,
         basisOfRecord, institutionCode, datasetName)

```

```{r}
#filter records to only Australia
records_filter_au <- records.2021.07.21 %>%
  filter(countryCode == "AU")
```

```{r}
#plot data on a map to get  view
library(ggplot2)
wm <- borders("world", colour="slategray1", fill="slategray1")
ggplot()+ coord_fixed()+ wm +
  geom_point(data = records_filter_au , aes(x = decimalLongitude, y = decimalLatitude),
             colour = "green", size = 0.5)+
  theme_bw()
```

#still some cleaning to do ^ but many points from North America and Asia are removed

```{r}
# get rid of records without coordinates as ALA did not get rid of all records without coordinates
records_filter_au_1  <- records_filter_au %>%
  filter(!is.na(decimalLongitude))%>%
  filter(!is.na(decimalLatitude))
```
#5334 records were removed ^


```{r}
#automatic cleaning algorithm of CoordinateCleaner
library(rnaturalearth)
#conversion of country code from ISO2c to ISO3c
records_filter_au_1$countryCode <-  countrycode(records_filter_au_1$countryCode, origin =  'iso2c', destination = 'iso3c')


#flag problems (won't include 'country' test as it flags all records)
records_filter_au_1 <- data.frame(records_filter_au_1)
flags <- clean_coordinates(x = records_filter_au_1 ,
                           lon = "decimalLongitude",
                           lat = "decimalLatitude",
                           countries = "countryCode",
                           species = "species",
                          tests = c("capitals", "centroids", "equal","gbif", "institutions",
                                    "zeros" )) 
summary(flags)
plot(flags, lon = "decimalLongitude", lat = "decimalLatitude")
```


#^  Flagged 1709 of 754717 records, but there is still cleaning to do 
```{r}
#now remove problematic records
dat_cl_aus <- records_filter_au_1[flags$.summary,]

#The flagged records
dat_fl_aus <- records_filter_au_1[!flags$.summary,]
```


```{r}
#plot flagged records

wm <- borders("world", colour="slategray1", fill="slategray1")
ggplot()+ coord_fixed()+ wm +
  geom_point(data = dat_fl_aus , aes(x = decimalLongitude, y = decimalLatitude),
             colour = "green", size = 0.5)+
  theme_bw()
```
#flagged records ^ like the one in the middle of the ocean above New Zealand are now removed 

```{r}
#Remove records with low coordinate precision 
#remove all records with a precision below 100 km
hist(dat_cl_aus$coordinateUncertaintyInMeters / 1000, breaks = 20)

dat_cl_aus <- dat_cl_aus %>%
  filter(coordinateUncertaintyInMeters / 1000 <= 100 | is.na(coordinateUncertaintyInMeters))

#Remove unsuitable data sources, 
table(dat_cl_aus$basisOfRecord)



dat_cl_aus <- filter(dat_cl_aus, basisOfRecord == "HUMAN_OBSERVATION" |
                         basisOfRecord == "OBSERVATION" |
                         basisOfRecord == "PRESERVED_SPECIMEN")
```


```{r}
#remove records with suspicious individual counts
table(dat_cl_aus$individualCount)
```

```{r} 
#remove records of absence i.e (individual count = 0) 
dat_cl_aus <- dat_cl_aus%>%
  filter(individualCount > 0 | is.na(individualCount))%>%
  filter(individualCount < 99 | is.na(individualCount)) 
```

```{r}
#plot flagged records

wm <- borders("world", colour="slategray1", fill="slategray1")
ggplot()+ coord_fixed()+ wm +
  geom_point(data = dat_cl_aus, aes(x = decimalLongitude, y = decimalLatitude),
             colour = "green", size = 0.5)+
  theme_bw()
```
# ^ now the records in China, Japan and the Philippines that were likely incorrectly labeled are removed 


```{r}
#export file
write.csv(dat_cl_aus,"/Users/jackhanigan/Documents/R/bigdata/BEES3041_BCI\\ecul_data.csv", row.names = FALSE)

```

