---
title: "Post_biodiverse_analysis"
author: "Jack Hanigan"
date: "31 July 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analyse phylogenetic endemism and phylogenetic diversity tests 


Load required libraries
```{r}
library(readr)
library(ggplot2)
library(hexbin)
library(ggpubr)
library(ggpmisc)
```

Put the csv files into lists
```{r}
file_list_clim <- list.files(path="/Users/jackhanigan/Downloads/Extracted data")

file_list_analysis <- list.files(path="/Users/jackhanigan/Downloads/Analysis")

```





load the climate csv files into r
```{r}
setwd("/Users/jackhanigan/Downloads/Extracted data")

for (i in 1:length(file_list_clim)) assign(file_list_clim[i], read_csv(file_list_clim[i]))
```


load the analysis csv files into r
```{r}

setwd("/Users/jackhanigan/Downloads/Analysis")

for (i in 1:length(file_list_analysis)) assign(file_list_analysis[i], read_csv(file_list_analysis[i]))
```


SCATTER PLOTS

plot Ang_CW_PE against climate variables
```{r}
plot(Ang_CW_PE.csv[["PE_CWE"]], Ang_bio2_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_CW_PE.csv[["PE_CWE"]], Ang_bio5_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_CW_PE.csv[["PE_CWE"]], Ang_bio6_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_CW_PE.csv[["PE_CWE"]], Ang_bio7_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_CW_PE.csv[["PE_CWE"]], Ang_bio12_at.csv[["wc2_mean"]], log = "xy")

```
plot Cor_CW_PE against climate variables
```{r}
plot(Cor_CW_PE.csv[["PE_CWE"]], Cor_bio1.csv[["wc2_mean"]], log = "xy")
plot(Cor_CW_PE.csv[["PE_CWE"]], Cor_bio5.csv[["wc2_mean"]], log = "xy")
plot(Cor_CW_PE.csv[["PE_CWE"]], Cor_bio6.csv[["wc2_mean"]], log = "xy")
plot(Cor_CW_PE.csv[["PE_CWE"]], Cor_bio7.csv[["wc2_mean"]], log = "xy")
plot(Cor_CW_PE.csv[["PE_CWE"]], Cor_bio12.csv[["wc2_mean"]], log = "xy")
```


plot Euc_CW_PE against climate variables
```{r}
plot(Euc_CW_PE.csv[["PE_CWE"]], Euc_bio1.csv[["wc2_mean"]], log = "xy")
plot(Euc_CW_PE.csv[["PE_CWE"]], Euc_bio5.csv[["wc2_mean"]], log = "xy")
plot(Euc_CW_PE.csv[["PE_CWE"]], Euc_bio6.csv[["wc2_mean"]], log = "xy")
plot(Euc_CW_PE.csv[["PE_CWE"]], Euc_bio7.csv[["wc2_mean"]], log = "xy")
plot(Euc_CW_PE.csv[["PE_CWE"]], Euc_bio12.csv[["wc2_mean"]], log = "xy")
```


plot Comb_CW_PE against climate variables
```{r}
plot(Comb_CW_PE.csv[["PE_CWE"]], Comb_bio1.csv[["wc2_mean"]], log = "xy")
plot(Comb_CW_PE.csv[["PE_CWE"]], comb_bio5.csv[["wc2_mean"]], log = "xy")
plot(Comb_CW_PE.csv[["PE_CWE"]], comb_bio6.csv[["wc2_mean"]], log = "xy")
plot(Comb_CW_PE.csv[["PE_CWE"]], Comb_bio7.csv[["wc2_mean"]], log = "xy")
plot(Comb_CW_PE.csv[["PE_CWE"]], Comb_bio12.csv[["wc2_mean"]], log = "xy")
```


plot Ang_phy_div angainst climate variables
```{r}
plot(Ang_phy_div.csv[["PD"]], Ang_bio2_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_phy_div.csv[["PD"]], Ang_bio5_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_phy_div.csv[["PD"]], Ang_bio6_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_phy_div.csv[["PD"]], Ang_bio7_at.csv[["wc2_mean"]], log = "xy")
plot(Ang_phy_div.csv[["PD"]], Ang_bio12_at.csv[["wc2_mean"]], log = "xy")

```


plot Cor_phy_div angainst climate variables
```{r}
plot(Cor_phy_div.csv[["PD"]], Cor_bio1.csv[["wc2_mean"]], log = "xy")
plot(Cor_phy_div.csv[["PD"]], Cor_bio5.csv[["wc2_mean"]], log = "xy")
plot(Cor_phy_div.csv[["PD"]], Cor_bio6.csv[["wc2_mean"]], log = "xy")
plot(Cor_phy_div.csv[["PD"]], Cor_bio7.csv[["wc2_mean"]], log = "xy")
plot(Cor_phy_div.csv[["PD"]], Cor_bio12.csv[["wc2_mean"]], log = "xy")

```

plot Euc_phy_div angainst climate variables
```{r}
plot(Euc_phy_div.csv[["PD"]], Euc_bio1.csv[["wc2_mean"]], log = "xy")
plot(Euc_phy_div.csv[["PD"]], Euc_bio5.csv[["wc2_mean"]], log = "xy")
plot(Euc_phy_div.csv[["PD"]], Euc_bio6.csv[["wc2_mean"]], log = "xy")
plot(Euc_phy_div.csv[["PD"]], Euc_bio7.csv[["wc2_mean"]], log = "xy")
plot(Euc_phy_div.csv[["PD"]], Euc_bio12.csv[["wc2_mean"]], log = "xy")

```

plot Comb_phy_div angainst climate variables
```{r}
plot(Comb_phy_div.csv[["PD"]], Comb_bio1.csv[["wc2_mean"]], log = "xy")
plot(Comb_phy_div.csv[["PD"]], comb_bio5.csv[["wc2_mean"]], log = "xy")
plot(Comb_phy_div.csv[["PD"]], comb_bio6.csv[["wc2_mean"]], log = "xy")
plot(Comb_phy_div.csv[["PD"]], Comb_bio7.csv[["wc2_mean"]], log = "xy")
plot(Comb_phy_div.csv[["PD"]], Comb_bio12.csv[["wc2_mean"]], log = "xy")

```

SCATTER PLOT REGRESSIONS


Comb5/CWPE regression (r=0.38)
```{r}
Comb5_CWPE <- ggplot(data=NULL, aes(x=comb_bio5.csv$wc2_mean, y=Comb_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point() +xlab('Bioclim5') +ylab('Eucalypt Phylogenetic Endemism') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())

my.formula <-y ~ x

Comb5_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
ggsave("Comb5_CWPE_scat.png")
```
Comb6/CWPE (r=0.14)
```{r}
Comb6_CWPE <- ggplot(data=NULL, aes(x=comb_bio6.csv$wc2_mean, y=Comb_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Comb6_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```

Euc6/CWPE (r=0.12)
```{r}
Euc6_CWPE <- ggplot(data=NULL, aes(x=Euc_bio6.csv$wc2_mean, y=Euc_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Euc6_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Euc5/CWPE (r=0.37)
```{r}
Euc5_CWPE <- ggplot(data=NULL, aes(x=Euc_bio5.csv$wc2_mean, y=Euc_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()+xlab('Bioclim5') +ylab('Eucalyptus Phylogenetic Endemism') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())

my.formula <-y ~ x

Euc5_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
ggsave("Euc5_CWPE_scat.png")
```
Euc12/CWPE (r=0.09)
```{r}
Euc12_CWPE <- ggplot(data=NULL, aes(x=Euc_bio12.csv$wc2_mean, y=Euc_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Euc12_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```

Cor5/CWPE (r=0.09)
```{r}


 Cor5_CWPE <- ggplot(data=NULL, aes(x=Cor_bio5.csv$wc2_mean, y=Cor_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

 my.formula <-y ~ x

 Cor5_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```


Cor6/CWPE (r=<0.01)
```{r}
Cor6_CWPE <- ggplot(data=NULL, aes(x=Cor_bio6.csv$wc2_mean, y=Cor_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Cor6_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Cor12/CWPE (r=0.11)
```{r}
Cor12_CWPE <- ggplot(data=NULL, aes(x=Cor_bio12.csv$wc2_mean, y=Cor_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Cor12_CWPE + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```

#phylo regression
Cor5_Phydiv(r=0.13)
```{r}

Cor5_Phydiv <- ggplot(data=NULL, aes(x=Cor_bio5.csv$wc2_mean, y=Cor_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()
my.formula <-y ~ x
Cor5_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```


Cor6_Phydiv(r=0.11)
```{r}
Cor6_Phydiv <- ggplot(data=NULL, aes(x=Cor_bio6.csv$wc2_mean, y=Cor_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Cor6_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Cor7_Phydiv(r=0.4)
```{r}
Cor7_Phydiv <- ggplot(data=NULL, aes(x=Cor_bio7.csv$wc2_mean, y=Cor_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Cor7_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Euc5_Phydiv(r=0.4)
```{r}
Euc5_Phydiv <- ggplot(data=NULL, aes(x=Euc_bio5.csv$wc2_mean, y=Euc_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point() +xlab('Bioclim5') +ylab('Eucalyptus Plylogenetic Diversity') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())

my.formula <-y ~ x

Euc5_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
ggsave("Euc5_Phydiv_scat.png")
```
Euc6_Phydiv(r=0.13)
```{r}
Euc6_Phydiv <- ggplot(data=NULL, aes(x=Euc_bio6.csv$wc2_mean, y=Euc_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Euc6_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Euc12_Phydiv(r=0.13)
```{r}
Euc12_Phydiv <- ggplot(data=NULL, aes(x=Euc_bio12.csv$wc2_mean, y=Euc_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Euc12_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Comb1_Phydiv(r=0.21)
```{r}
Comb1_Phydiv <- ggplot(data=NULL, aes(x=Comb_bio1.csv$wc2_mean, y=Comb_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Comb1_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Comb5_Phydiv(r=0.35)
```{r}
Comb5_Phydiv <- ggplot(data=NULL, aes(x=comb_bio5.csv$wc2_mean, y=Comb_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point() +xlab('Bioclim5') +ylab('Eucalypt Phylogenetic Diversity') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())

my.formula <-y ~ x

Comb5_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
ggsave("Comb5_Phydiv_scat.png")
```
Comb6_Phydiv(r=0.07)
```{r}
Comb6_Phydiv <- ggplot(data=NULL, aes(x=comb_bio6.csv$wc2_mean, y=Comb_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Comb6_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
Comb12_Phydiv(r=0.22)
```{r}
Comb12_Phydiv <- ggplot(data=NULL, aes(x=Comb_bio12.csv$wc2_mean, y=Comb_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') + geom_smooth(method=lm) + geom_point()

my.formula <-y ~ x

Comb12_Phydiv + stat_poly_eq(formula=my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)
```
HEX PLOTS

Comb5 PD Hex
```{r}
Comb5_Phydiv_hex <- ggplot(data=NULL, aes(x=comb_bio5.csv$wc2_mean, y=Comb_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') +xlab('Bioclim5') +ylab('Eucalypt Phylogenetic Diversity') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())
Comb5_Phydiv_hex + geom_hex(bins=35) +scale_fill_gradient(low="springgreen2",high="steelblue1") +theme_bw()
ggsave('Comb5_PD_hex.png')
```


Comb5 PE Hex
```{r}
Comb5_CWPE_hex <- ggplot(data=NULL, aes(x=comb_bio5.csv$wc2_mean, y=Comb_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') +xlab('Bioclim5') +ylab('Eucalypt Phylogenetic Endemism') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())
Comb5_CWPE_hex + geom_hex(bins=35) +scale_fill_gradient(low="springgreen2",high="steelblue1") +theme_bw()
ggsave('Comb5_PE_hex.png')
```


Euc5 PD Hex
```{r}
Euc5_Phydiv_hex <- ggplot(data=NULL, aes(x=Euc_bio5.csv$wc2_mean, y=Euc_phy_div.csv$PD)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') +xlab('Bioclim5') +ylab('Eucalyptus Phylogenetic Diversity') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())
Comb5_Phydiv_hex + geom_hex(bins=35) +scale_fill_gradient(low="springgreen2",high="steelblue1") +theme_bw()
ggsave('Euc5_PD_hex.png')
```


Euc5 PE Hex
```{r}
Euc5_CWPE_hex <- ggplot(data=NULL, aes(x=Euc_bio5.csv$wc2_mean, y=Euc_CW_PE.csv$PE_CWE)) + scale_x_continuous(trans = 'log') + scale_y_continuous(trans = 'log') +xlab('Bioclim5') +ylab('Eucalyptus Phylogenetic Endemism') + theme(axis.text.x = element_blank(),axis.text.y = element_blank())
Comb5_CWPE_hex + geom_hex(bins=35) +scale_fill_gradient(low="springgreen2",high="steelblue1") +theme_bw()
ggsave('Euc5_PE_hex.png')
```



